Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-11-24 contents/draft.tex
Enter Key

    \abstract[Abstract]{Korean morphological analysis is a fundamental step in analyzing the Korean language. Owing to the nature of Korean agglutinative words, building an automatic analysis system is difficult because parts-of-speech tagging independently is insufficient to complete analysis, as in English. In addition, various methods for morphological analysis have been proposed; however, efficient methods, such as BPE (Byte Pair Encoding), are mainly used in applications intended to be used as tokenizers for deep learning. In this study, we propose a method to maximize the performance of an efficient morphological analysis system that can be used for tokenization through multi-stage re-ranking based on deep learning. For cases whose rankings have been changed through re-ranking, it is feasible to improve the performance while maintaining speed by updating the cost matrix of the lattice-based morphological analysis system. Through experiments, we demonstrate that the proposed method effectively improves performance via reducing errors by over 30\% in both spoken and written language models.}
    \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, re-ranking}

@@

    We transformed this organized morphological corpus using the training–example transformation process described in Section ~\ref{subsec3.2} to generate samples for training the dictionary-based morphological analysis model.

>>>>

    \abstract[Abstract]{
        Korean morphological analysis is a fundamental step in analyzing the Korean language.
        Owing to the nature of Korean agglutinative words, building an automatic analysis system is difficult because parts-of-speech tagging independently is insufficient to complete analysis, as in English.
        In addition, various methods for morphological analysis have been proposed; however, efficient methods, such as BPE (Byte Pair Encoding), are mainly used in applications intended to be used as tokenizers for deep learning.
        In this study, we propose a method to maximize the performance of an efficient morphological analysis system that can be used for tokenization through multi-stage re-ranking based on deep learning.
        For cases whose rankings have been changed through re-ranking, it is feasible to improve the performance while maintaining speed by updating the cost matrix of the lattice-based morphological analysis system.
        Through experiments, we demonstrate that the proposed method effectively improves performance via reducing errors by over 30\% in both spoken and written language models.
    }
    \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, re-ranking}

@@

    We transformed this organized morphological corpus using the training-example transformation process described in Section ~\ref{subsec3.2} to generate samples for training the dictionary-based morphological analysis model.
